---
title: "Final Project"
output: pdf_document
---
```{r, message=FALSE}
library(tidyverse)
library(readr)
library(readxl)
library(GGally)
library(mgcv)
library(ggplot2)
library(glmnet)
library(caret)
library(modelr)
library(mgcv)
```

## Load Data
```{r}
data <- readxl::read_excel("body_density_data.xlsx") %>%
  select (-bodyfat_brozek, -bodyfat_siri, -id)
```


## Descriptive Statistics

```{r}
summary(data)
```

```{r, message = FALSE}
ggpairs(data)
```


Outcome: body_density (easy to interpret)

neck, ankle, abdomen, weight might need transformation
--> natural log/ box-cox 

neck
```{r}
hist(data$neck)
```
It's just an outlier 

ankle
```{r}
hist(data$ankle)
```

```{r}
hist(data$abdomen)
```

weight
```{r}
hist(data$weight)
```
All outliers above are denoting a specific group of participants.

Participant #39 is an outlier. This participant has outlying measurement for weight and abdomen. Since he/she also has a larger chest circumference, the data point is less likely to be a measurement error. It could has useful info.

--> no transformation for all X's 



## Variable Selection 
### Backward 
```{r}
mult.fit <- lm(body_density ~ ., data = data)
step(mult.fit, direction='backward')
```

### forward 
```{r}
intercept_only_fit <- lm(body_density ~ 1, data=data)
step(intercept_only_fit, direction = 'forward', scope = formula(mult.fit))
```
### Both
```{r}
step(intercept_only_fit, direction = 'both', scope = formula(mult.fit), data = data)
```

### lasso 
```{r}
set.seed(200)
lamba_seq <- 10^seq(-3, 0,by = .1)
train_predictors <- data %>% select(-body_density)
cv_object <- cv.glmnet(as.matrix(train_predictors), data$body_density,
                    lambda = lamba_seq, nfolds = 10)
```

```{r}
tibble(lambda  = cv_object$lambda,
       mean_cv_error = cv_object$cvm) %>%
  ggplot(aes(x = lambda, y = mean_cv_error)) +
  geom_point()
```
```{r}
cv_object$lambda.min
```
```{r}
lasso_fit <- glmnet(as.matrix(train_predictors),
                    data$body_density,
                    lambda = cv_object$lambda.min)
coef(lasso_fit)
```

## Cross Validation
```{r}
cv_df =
  crossv_mc(data, 5) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    backward_mod  = map(train, ~lm(body_density ~ age + weight + neck + abdomen + hip + thigh + bicep + forearm + wrist, data = .x)),
    both_forward_mod  = map(train, ~lm(body_density ~ abdomen + weight + wrist + forearm + bicep + neck, data = .x)),
    lasso_mod  = map(train, ~lm(body_density ~ age + height + abdomen + wrist, data = as_tibble(.x)))) %>% 
  mutate(
    rmse_backward = map2_dbl(backward_mod, test, ~rmse(model = .x, data = .y)),
    rmse_both_forward  = map2_dbl(both_forward_mod, test, ~rmse(model = .x, data = .y)),
    rmse_lasso = map2_dbl(lasso_mod, test, ~rmse(model = .x, data = .y)))
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) +
  ggtitle("Model Performance in Cross Validation", 
          subtitle = "backward selection variabls: age, weight, neck, abdomen, hip, thigh, bicep, forearm, wrist \nforward selection, setpwise regression variables: abdomen, weight, wrist, forearm,  bicep, neck \nlasso regression variables: age, height, abdomen, wrist") +
  ylab("Root Mean Squared Eroor") +
  xlab("Model") +
  theme(plot.subtitle=element_text(size=9, color = "darkgray"))
```
```{r}
rmse <- cv_df %>% 
  select(starts_with("rmse"))

sapply(rmse, mean, na.rm = T)
```


adj r^2
```{r}
lm(body_density ~ age + weight + neck + abdomen + hip + thigh + bicep + forearm + wrist, data = data)  %>% summary()
```
```{r}
lm(body_density ~ abdomen + weight + wrist + forearm + bicep + neck, data = data) %>% summary()
```

```{r}
lm(body_density ~ age + height + abdomen + wrist, data = data) %>% summary()
```

final model: both + forward

```{r}
final <- lm(body_density ~ abdomen + weight + wrist + forearm + bicep + neck, data = data)
par(mfrow = c(2,2))
plot(final)
```

```{r}
library(car)
vif(final)
```
```{r}
mean((data$body_density - predict.lm(final, data)) ^ 2)
```